Group meetings

### 2023-07-10 diapo/10-07-23_meeting/main.tex
Prez de ce soir

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{c p{0.3\textwidth} c p{0.3\textwidth} c}
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
      1 & Find another LSTM problem & On going & Didn't find & Yes\\
      2 & Find out what is causing the issue & Partly & I had a scale of 10000 and reduced it to 1.5 & No\\
      3 & Find formula for approximate onChip area & No & Can be done later & No\\
      4 & Work on thesis & On going & & No\\
    \end{tabular}

@@

  \begin{frame}{What's new}
    \begin{itemize}
      \item Results obtianed :
        \begin{itemize}
            \color{text}
          \item I reduced the factor of the results
          \item The factor is now tolerable, will have to see how it behaves with other problems
        \end{itemize}
      \item Improvements :
        \begin{itemize}
            \color{text}
          \item Reduce the still existing factor
        \end{itemize}
      \item Relevant information :
        \begin{itemize}
            \color{text}
          \item I reduced the factor to 16 first, and then to 1.5.
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{What's new}
    Here the scale factor is almost the same with the serialized and parallel version (1.50 vs 1.58).
    \includegraphics[width=\textwidth]{output/factor1.5.png}
  \end{frame}

  \begin{frame}{What's new}
    Today, I managed to reduce the scale factor even more. (1.21)
    \includegraphics[width=\textwidth]{output/factor1.2.png}
  \end{frame}

  \begin{frame}
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item The results are still not quite right.
      \item I am wondering whether it is still due to the activation function circuit.
    \end{itemize}
  \end{frame}

  \begin{frame}{Problems/doubts}
    I had to train using custom activation function but still not perfect.
    \begin{figure}[!tbp]
      \centering
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/sigmoid}
        \caption{ $Sigmoid(x)$ - RSME : 0.0051}
      \end{minipage}
      \hspace{20pt}
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/cSigmoid}
        \caption{ $ Sigmoid(0.67\cdot x) $ - RSME : 0.0014}
      \end{minipage}
      \caption{Sigmoid}
    \end{figure}
  \end{frame}

  \begin{frame}{Problems/doubts}
    I had to train using custom activation function but still not perfect.
    \begin{figure}[!tbp]
      \centering
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/tanh}
        \caption{ $ Tanh(x) $ - RSME : 0.022}
      \end{minipage}
      % \rightarrow
      \hspace{20pt}
      \begin{minipage}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{activation/cTanh}
        \caption{ $2\cdot Sigmoid(0.67\cdot x)-1$ - RSME : 0.0029}
      \end{minipage}
      \caption{Tanh}
    \end{figure}
  \end{frame}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      0.1 & Formula onChip Area \\
      0.2 & power consumption \\
      1 & Find another LSTM problem \\
      1.1 & Mbedded Video stabilization \\
      2 & Digital inference time \\
    \end{tabular}
  \end{frame}

>>>>

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{c p{0.3\textwidth} c p{0.3\textwidth} c}
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
      0 & Work on thesis & onGoing & & No\\
      0.1 & Formula onChip Area & Almost & & No\\
      0.2 & power consumption & No & How would I approximate ? & Yes \\
      1 & Find another LSTM problem & Yes and no & Found one but too complicated & No\\
      1.1 & Mbedded Video stabilization & Yes & & No\\
      2 & Digital inference time & No & & No\\
    \end{tabular}

@@

  \begin{frame}{What's new}
    \begin{itemize}
      \item Results obtianed :
        \begin{itemize}
            \color{text}
          \item
        \end{itemize}
      \item Improvements :
        \begin{itemize}
            \color{text}
          \item
        \end{itemize}
      \item Relevant information :
        \begin{itemize}
            \color{text}
          \item I started really focusing on the writing of the thesis. I'll have few to no updates from now on. (No idea what else to do)
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Problems/doubts}
    I am wondering what goes in the :
    \begin{itemize}
      \item abstract
      \item thesis outline
    \end{itemize}
  \end{frame}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      0.1 & Formula onChip Area \\
      0.2 & power consumption \\
      1 & Find another LSTM problem (optionnal) \\
      2 & Digital inference time \\
    \end{tabular}
  \end{frame}
